GetTrendsData.Rmd

### 2014-09-16 DataManipulation/DataManipulation.Rmd
Added in the August data.

---
title: "DataCleaning"
author: "James Woods"
date: "07/24/2014"
output: html_document
---
Load in the Trends data.
```{r}

@@

#Get the names of the trend files
TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData")
#Removing the subdirectory
TrendsFiles[-12]

#all the trends in one data frame
AllTrends<-as.data.frame(lapply(TrendsFiles[-12],FUN=ReadTrends))

>>>>

---
title: "DataCleaning"
author: "James Woods"
date: "07/24/2014"
output: html_document
---
Load data is from http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-data.aspx

Forecasts are from

http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-forecasts.aspx

Load in the Trends data.
```{r}
# Data is from
Load data is from http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-data.aspx

Forecasts are from

http://www.pjm.com/markets-and-operations/ops-analysis/historical-load-forecasts.aspx

@@

#Get the names of the trend files
TrendsFiles<-list.files("~/Research/Forecast-Peak-With-Google-Trends/TrendsData", pattern="*.W.csv",all.files= FALSE)

#all the trends in one data frame
AllTrends<-as.data.frame(lapply(TrendsFiles,FUN=ReadTrends))

### 2014-09-16 ResearchNotes/GetTrendsData.Rmd
Added in the August data.

Google Trend Links
========================================================
These will get google trends for most of the stats in the PJM teritory.

@@

>>>>

---
title: "GetTrendsData.Rmd"
author: "James Woods"
date: "09/11/2014"
output: html_document
---
Google Trend Links
========================================================
These will get google trends for most of the stats in the PJM teritory.

@@

http://www.google.com/trends/explore#q=gas&date=today%203-m&cmpt=q
http://www.google.com/trends/explore#q=Movie&date=today%203-m&cmpt=q
http://www.google.com/trends/explore#q=News&date=today%203-m&cmpt=q
http://www.google.com/trends/explore#q=Restaurant&date=today%203-m&cmpt=q
http://www.google.com/trends/explore#q=Traffic&date=today%203-m&cmpt=q
